Title of the paper

### 2023-07-09 2023/ITMO paper/elsarticle-template-num.tex
test algorithm

>>>>

\begin{algorithm}
 \LinesNumbered
 \KwIn{this text}
 \KwOut{how to write algorithm with \LaTeX2e }
 Initialize $k=1$\\
 \While{ $\Delta_t \geq \epsilon$ and  $k \leq K_{max}$}{
  Calculate the estimate of the H\"older constant $m$ from (\ref{eq:19}) using $A_k$\\
	\For{$i=1$ \KwTo $k$}{
	g\\
	}

  \eIf{understand}{
   go to next section\\
   current section becomes this one
   }{
   go back to the beginning of current section
  }
 $k = k + 1$\\
 }
 \KwRet{$y_{min}$}
 \caption{Global search}
\end{algorithm}
